Measurement of deeply virtual Compton scattering off Helium-4 with CLAS at Jefferson Lab

### 2020-10-20 eg6-letters/long-paper/prc-dvcshelium.tex
Small changes

\begin{figure}[tbp!]
\center
\includegraphics[width=10.0cm]{fig1/GPD.png}
\caption{General representation for the GPDs of a nucleon represented by the triple lines and noted $N$.
	Single lines can represent quarks or anti-quarks probed in the nucleon.}
\label{fig:GPD}
\end{figure}

@@

Since, DVCS is a 
process selected using tight exclusivity constrains, some of the initial and final-state effects are
automatically mitigated. Selection criterion on missing energy and momentum are performed,
constraining the range of initial Fermi motion and final interactions possible. However, no theoretical
calculation is available to correct for the reminder of these effects yet. Modern calculations exist 
for such effects in DIS \cite{Cosyn:2017ekf} and quasi-elastic \cite{Ethier:2014bua}
and we can expect them to be extended to the DVCS 
process as more data becomes available. Another avenue of progress
on this topic will be the use of experimental techniques like tagging. This process
can help to control both initial and final state effects by detecting the nuclear remnant.
In the tagged process the target breaks in two providing directly the initial state
of the struck nucleon, while measured backward nuclear fragments limit significantly the
impact of final state effects.

@@

An important issue with the HERMES measurement and how it is obtained from data has been raised in
\cite{Guzey:2003jh} to explain the discrepancy with theoretical expectations.
The main concern is that the DVCS process is not fully detected and the scattered target
is instead reconstructed through a missing mass measurement of the other reaction products. The 
issue with this method is that the detector resolution is not good enough to separate the 
coherent and incoherent channels properly. 
Instead, the results are labeled "coherent enriched" and "incoherent enriched" at low and high 
$-t$, respectively. This label is based on the assumption that the very different behavior of the
cross sections of the two channels in $t$ will lead to a clear differentiation. However, the
results in Fig. \ref{fig:HERMES2} show similar behaviors in both sectors of $t$, which  
challenges this assumption and could explain the tension between theory and experiment.

@@

In principle, 
a selection based only on the missing energy of the system would be
enough to guarantee the 
exclusivity of the process. However, in our experiment, where particles 
are detected at very different energies and with very different detector 
resolutions, this method would not be optimal. For instance the momentum 
of the helium nuclei is negligible in the missing energy observable, thus
this valuable information has no impact on a selection using this observable only.
To circumvent this issue, we constrain the selection of our exclusive events by using seven 
variables selected to optimize the use of all the detector information available. 
The seven variables are defined as follow for the coherent 
DVCS (replace helium by proton for the incoherent case):
\begin{itemize}
	\item Co-planarity ($\Delta \phi$) of the virtual photon, the real photon and
		the recoil helium, defined as the angle between the helium, virtual photon
		plane and the virtual photon, real photon plane;
	\item Missing energy of the full system;
	\item Missing mass of the full system;
	\item Missing transverse momentum of the full system;
	\item Missing mass of the electron-helium system;
	\item Missing mass of the electron-photon system;
	\item Co-linearity ($\theta$) of the measured photon with the missing momentum of the 
		electron-helium system.
\end{itemize}

@@

\begin{figure}[tbp]
\includegraphics[width=8cm]{fig3/T_ratio_pi0_dvcs_Coh_t.pdf}
\includegraphics[width=8cm]{fig3/T_ratio_pi0_dvcs_InCoh_t.pdf}
\caption{The coherent (left) and incoherent (right) $\pi^{0}$ 
contamination estimated in the DVCS events as a function of the 
transfered momentum squared -$t$ and integrated over the kinematical 
variables $Q^2$, $x_B$, and $\phi$.}
\label{fig:cont_yield}
\end{figure}

>>>>

\begin{figure}[tbp!]
\center
\includegraphics[width=10.0cm]{fig1/GPD.png}
\caption{General representation for the GPDs of a nucleon represented by the triple lines and noted $N$.
	Single lines can represent quarks or anti-quarks probed in the nucleon shown by the triple lines.}
\label{fig:GPD}
\end{figure}

@@

Since, DVCS is a 
process selected using tight exclusivity constrains, some of the initial and final-state effects are
automatically mitigated. Selection criterion on missing energy and momentum are performed,
constraining the range of initial Fermi motion and final interactions possible. However, no theoretical
calculation is available to correct for the reminder of these effects yet. Modern calculations exist 
for such effects in DIS \cite{Cosyn:2017ekf} and quasi-elastic scattering \cite{Ethier:2014bua}
and we can expect them to be extended to the DVCS 
process as more data becomes available. Another avenue of progress
on this topic will be the use of experimental techniques like tagging. This process
can help to control both initial and final state effects by detecting the nuclear remnant.
In the tagged process the target breaks in two providing directly the initial state
of the struck nucleon, while measured backward nuclear fragments limit significantly the
impact of final state effects.

@@

An issue with the HERMES measurement and how it is obtained from data has been raised in
\cite{Guzey:2003jh} to explain the discrepancy with theoretical expectations.
The main concern is that the DVCS process is not fully detected and the scattered target
is instead reconstructed through a missing mass measurement of the other reaction products. The 
issue with this method is that the detector resolution is not good enough to separate the 
coherent and incoherent channels properly. 
Instead, the results are labeled "coherent enriched" and "incoherent enriched" at low and high 
$-t$, respectively. This label is based on the assumption that the very different behavior of the
cross sections of the two channels in $t$ will lead to a clear differentiation. However, the
results in Fig. \ref{fig:HERMES2} show similar behaviors in both sectors of $t$, which  
challenges this assumption and could explain the tension between theory and experiment.

@@

In principle, 
a selection based only on the missing energy of the system would be
enough to guarantee the 
exclusivity of the process. However, in our experiment, where particles 
are detected at very different energies and with very different detector 
resolutions, this method would not be sufficient. For instance the momentum 
of the helium nuclei is negligible in the missing energy observable, thus
this valuable information has no impact on a selection using this observable only.
To circumvent this issue, we constrain the selection of our exclusive events by using seven 
variables selected to optimize the use of all the detector information available. 
The seven variables are defined as follow for the coherent 
DVCS (replace helium by proton for the incoherent case):
\begin{itemize}
	\item Co-planarity ($\Delta \phi$) of the virtual photon, the real photon and
		the recoil helium, defined as the angle between the helium, virtual photon
		plane and the virtual photon, real photon plane;
	\item Missing energy of the full system;
	\item Missing mass of the full system;
	\item Missing transverse momentum of the full system;
	\item Missing mass of the electron-helium system;
	\item Missing mass of the electron-photon system;
	\item Co-linearity ($\theta$) of the measured photon with the missing momentum of the 
		electron-helium system.
\end{itemize}

@@

\begin{figure}[tbp]
\includegraphics[width=8cm]{fig3/T_ratio_pi0_dvcs_Coh_t.pdf}
\includegraphics[width=8cm]{fig3/T_ratio_pi0_dvcs_InCoh_t.pdf}
\caption{The coherent (left) and incoherent (right) $\pi^{0}$ 
contamination estimated in the DVCS events as a function of the 
transferred momentum squared -$t$ and integrated over the kinematical 
variables $Q^2$, $x_B$, and $\phi$.}
\label{fig:cont_yield}
\end{figure}
